An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Pass over new conclusion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
\paragraph{Summary.}
This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.  % the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.

This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e. piecewise linear convex) loss functions.
We also saw that it is a general technique that can be used for any finite elicitable property.

Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
\jessie{Add more?}

@@

\paragraph{Directions.}
There are several direct open questions involving the dimension of the surrogate loss.
It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
%Another direction is additional lower bound techniques, or further development of our necessary conditions.

This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
We would also like to move toward a full understanding of the differences between these classes.
For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
These questions have both theoretical interest and potential practical significance.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
\paragraph{Summary.}
\jessiet{Old conclusion commented out.}
In this paper, we formalize a very intuitive way of designing convex surrogate losses for classification-like problems-- by embedding the outcomes into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).

We then proceed to construct a calibrated link function from a surrogate to the discrete loss it embeds, showing the consistency of our surrogates.
\jessie{Elaborate?}

We conclude with examples of how the embedding framework presented can be applied to understand surrogates given in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz Hinge.
We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we examine when \jessie{How to concisely explain what we do for Lov\'asz?}

%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.  % the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
%
%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e. piecewise linear convex) loss functions.
%We also saw that it is a general technique that can be used for any finite elicitable property.
%
%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
%\jessie{Add more?}

@@

\paragraph{Directions.}
One open question of particular interest involves the dimension of the input to a surrogate; given a discrete loss, can we construct the surrogate that embeds it \emph{of minimal dimension}?
Often, we na\"ively embed the reports into an $n$-dimensional space, so the dimensionality of the problem increases with the number of possible labels.
As the dimension of the optimization problem is a function of this \emph{embedding dimension}, it is important to characterize when we can reduce the dimension of our embedding.
%There are several direct open questions involving the dimension of the surrogate loss.
%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
%Another direction is additional lower bound techniques, or further development of our necessary conditions.

%This paper also suggests an agenda of defining more nuanced classes of surrogate losses and studying their properties.
%For example, a tangential topic in this work was the characteristics of a ``good'' link function; formalizing and exploring this question is an exciting direction.
%We would also like to move toward a full understanding of the differences between these classes.
%For example, how does embedding dimension compare in general to convex elicitation dimension (the dimensionality $d$ required of \emph{any} convex surrogate loss)?
%These questions have both theoretical interest and potential practical significance.
